---
title: "hw3md"
author: "Juan Silva"
date: "5/16/2019"
output: html_document
---

```{r}

library(tidyverse)
library(stargazer)

df1 <- read_csv("HW3Data.csv")

```


1. Create a linear probability model that predicts a respondent’s probability of voting ‘yes’ on the
ballot based on their age, income, NEP score, the risk reduction offered by the program, and the
cost of the program to that respondent. Show the model and interpret the regression
coefficients.

Data columns are: (1) “risk”: level of risk reduction, (2) “bid”: annual payment for the household, (3) “vote”: 1 is
yes, 0 is no, (4)”NEP” : measure of environmental concern (feel free to consult the WhaleStrikes Group Project report for more information), (5) ”income”: categorical variable for income level, (6)”age”: categorical variable for
age.

```{r, results="asis"}
lm1 <- lm(vote ~ age + income + NEP + risk + bid, data=df1)

lm1

stargazer(lm1, type="html",
          title = "models")

# Vote = 0.1196977 + 0.0099816*agetofifty - 0.0201190*agetoforty - 0.0162261*agetosixty + 0.0204401*agetothirty + 0.0088282*incomeone_percent + 0.0027386*incomepoor + 0.0074891*incomerich + 0.0467922*incomevery_rich + 0.0158639*NEP + 0.0007445*risk - 0.0010699*bid 




# Over sixty and middle are the reference groups.

summary(lm1)

```


2. Based on this regression, what can you say about the value of a single prevented whale death?
(Hint: Think about how risk reduction for all whales translates into the number of whale deaths
avoided)

```{r}

# We used our first model and solved for bid, getting the following equation:
# bid = (0.1196977 + 0.0099816*agetofifty - 0.0201190*agetoforty - 0.0162261*agetosixty + 0.0204401*agetothirty + 0.0088282*incomeone_percent + 0.0027386*incomepoor + 0.0074891*incomerich + 0.0467922*incomevery_rich + 0.0158639*NEP + 0.0007445*risk - Vote)/0.0010699

# We created a function to calculate for a specific indidivual, and replaced the values in the function to obtain "bid" for this individual given a 20% risk reduction versus a 24% reduction (4% of risk reduction means an increase of 1 whale saved).

bidfunc00 <- function(bid){(0.1196977 + 0.0099816*agetofifty - 0.0201190*agetoforty - 0.0162261*agetosixty + 0.0204401*agetothirty + 0.0088282*incomeone_percent + 0.0027386*incomepoor + 0.0074891*incomerich + 0.0467922*incomevery_rich + 0.0158639*NEP + 0.0007445*risk - vote)/0.0010699}

# For individual #1

bidfunc01 <- function(bid){(0.1196977 + 0.0099816*0 - 0.0201190*0 - 0.0162261*0 + 0.0204401*1 + 0.0088282*0 + 0.0027386*0 + 0.0074891*0 + 0.0467922*1 + 0.0158639*15 + 0.0007445*20 - 0)/0.0010699}

bidfunc02 <- function(bid){(0.1196977 + 0.0099816*0 - 0.0201190*0 - 0.0162261*0 + 0.0204401*1 + 0.0088282*0 + 0.0027386*0 + 0.0074891*0 + 0.0467922*1 + 0.0158639*15 + 0.0007445*24 - 0)/0.0010699}

# From risk 20 to 24, bid changes from 411.0464 to 413.8298, which means tthe value of a single prevented whale death is around 2.783438.



# lm2 <- lm(bid ~ age + income + NEP + risk + vote, data=df1)
# 
# summary(lm2)
# 
# # bid = 70.25203 - 4.38308*agetofifty - 5.28253*agetoforty - 8.43575*agetosixty - 1.83242*agetothirty - 1.31112*incomeone_percent + 1.04449*incomepoor + 0.50045*incomerich - 1.14663*incomevery_rich - 0.04160*NEP - 0.04014*risk - 5.02885*vote
# 
# bidfunc <- function(bid){70.25203 - 4.38308*agetofifty - 5.28253*agetoforty - 8.43575*agetosixty - 1.83242*agetothirty - 1.31112*incomeone_percent + 1.04449*incomepoor + 0.50045*incomerich - 1.14663*incomevery_rich - 0.08160*NEP - 0.04014*risk - 5.02885*vote}
# 
# # For individual 1:
# 
# bidfunc1 <- function(bid){70.25203 - 4.38308*0 - 5.28253*0 - 8.43575*0 - 1.83242*1 - 1.31112*0 + 1.04449*0 + 0.50045*0 - 1.14663*1 - 0.04160*15 - 0.04014*20 - 5.02885*0}
# 
# bidfunc2 <- function(bid){70.25203 - 4.38308*0 - 5.28253*0 - 8.43575*0 - 1.83242*1 - 1.31112*0 + 1.04449*0 + 0.50045*0 - 1.14663*1 - 0.04160*15 - 0.04014*24 - 5.02885*0}
# 
# # For individual 2:
# 
# bidfunc3 <- function(bid){70.25203 - 4.38308*agetofifty - 5.28253*agetoforty - 8.43575*agetosixty - 1.83242*agetothirty - 1.31112*incomeone_percent + 1.04449*incomepoor + 0.50045*incomerich - 1.14663*incomevery_rich - 0.08160*NEP - 0.04014*risk - 5.02885*vote}
# 
# 
# df2 <- df1 %>% 
#   mutate(whales = risk/4)
# 
# lm3 <- lm(bid ~ age + income + NEP + risk + vote + whales, data=df2)
# 
# lm3



```


3. Pick three arbitrary respondents. For each of those respondents, estimate their WTP for a VSR
program offering 60% risk reduction.

```{r}

# This one is model 1 rearranged for bid

bidfunc03 <- function(bid){(0.1196977 + 0.0099816*agetofifty - 0.0201190*agetoforty - 0.0162261*agetosixty + 0.0204401*agetothirty + 0.0088282*incomeone_percent + 0.0027386*incomepoor + 0.0074891*incomerich + 0.0467922*incomevery_rich + 0.0158639*NEP + 0.0007445*risk - vote)/0.0010699}




```



4. Now repeat this process and estimate the mean WTP for a VSR program offering 60% risk
reduction among Santa Barbara County households.


```{r}

bidfunc04 <- function(bid){(0.1196977 + 0.0099816*agetofifty - 0.0201190*agetoforty - 0.0162261*agetosixty + 0.0204401*agetothirty + 0.0088282*incomeone_percent + 0.0027386*incomepoor + 0.0074891*incomerich + 0.0467922*incomevery_rich + 0.0158639*NEP + 0.0007445*risk - vote)/0.0010699}


# mode of age
# mode of income
# mean of NEP
# vote 0.5

```



5. If there are 150,000 households in Santa Barbara County, estimate the total benefit of a VSR
program to these households.


```{r}



```


6. Based only on these benefits, do the benefits of the VSR program outweigh the costs?

```{r}



```





